MLExplain

### 2018-07-23 paper.tex
I think I have addressed everything

%\documentclass{article}
\documentclass[twocolumn,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[top=1cm, bottom=2cm, left=1.5cm, right=1.5cm]{geometry} 
\usepackage{minted}
\usepackage{tikz}
\usetikzlibrary{positioning,fit,shapes,arrows.meta}
\usepackage{hyperref}

@@

We now motivate our design choices. First, we use JavaScript because MLExplain
is a witness that JSExplain can easily be adapted to other languages, by
providing three components: an interpreter written in the subset of OCaml that
our compiler supports, a parser of the language, and a library to display OCaml
values. It would be possible to sever all links to the infrastructure provided
by JSExplain, but this would require significant work.

It is possible to use an existing debugger to explore how an interpreter works.
This is how we initially debugged our JavaScript interpreter and this was the
motivation to start working on JSExplain. Indeed, our interpreter is written as
a purely functional set of recursive functions that extensively use monadic
operations implemented in continuation passing style. It is difficult to
correctly navigate such functions, as stepping over a continuation means
reaching the end of the program. One thus has to be aware of whether a function
call is a continuation or a usual function. In addition, we did not find an easy
way to display the state of the interpreted program, even when relying on the
use of fixed names for the term, the state, and the context.

@@

As future work, we plan to extend the subset of OCaml supported by our compiler,
to be able to directly use the standard library when writing interpreters, and
to implement the few OCaml construct missing from our interpreter. We also want
to improve the web interface and to allow the user to load code from multiple files.

>>>>

%\documentclass{article}
\documentclass[twocolumn,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[top=1.5cm, bottom=2cm, left=2cm, right=2cm]{geometry} 
\usepackage{minted}
\usepackage{tikz}
\usetikzlibrary{positioning,fit,shapes,arrows.meta}
\usepackage{hyperref}

@@

We now motivate our design choices. First, we use JavaScript because MLExplain
is a witness that JSExplain can easily be adapted to other languages, by
providing three components: an interpreter written in the subset of OCaml that
our compiler supports, a parser of the language, and a library to display
runtime values. It would be possible to sever all links to the infrastructure
provided by JSExplain, but this would require significant work.

Second, it is possible to use an existing debugger to explore how an interpreter
works. This is how we initially debugged our JavaScript interpreter and this was
the motivation to start working on JSExplain. Indeed, our interpreter is written
as a purely functional set of recursive functions that extensively use monadic
operations implemented in continuation passing style. It is difficult to
correctly navigate such functions, as stepping over a continuation means
reaching the end of the program. One thus has to be aware of whether a function
call involves a continuation or a usual function. In addition, we did not find
an easy way to display the state of the interpreted program, even when relying
on the use of fixed names for the term, the state, and the context. The use of
fixed names may seem fragile, but as we only rely on a few of them and as the
signature of the evaluation functions are uniform, we have not observed any
issue with this approach.

@@

As future work, we plan to extend the subset of OCaml supported by our compiler,
to be able to directly use the standard library when writing interpreters. We
also plan to implement the few OCaml construct missing from our interpreter for
lack of time, such as record patterns and objects. It would be most useful to
document the evaluation order of every OCaml construction to make sure our
interpreters follows it. Finally, be want to improve the web interface and to
allow the user to load code from multiple files.
